\thetitle

### 2025-05-13 workshop/TPG.tex
typo

But this is where Pigeons can help: within a Parallel Tempering (PT) run, PG can be
used to explore each distribution in an annealing sequence that interpolates between
the prior and posterior. We expect PG to work more effectively on tempered 
distributions closer to the prior. Such samples can then be transported towards 
the posterior chain via the PT process.
In order to construct this sequence of distributions for an arbitrary program in
a Turing-complete PPL, it suffices to inject an inverse temperature parameter 
$\beta\in[0,1]$ in the call to compute the log density of every \texttt{observe} 
statement in the program. Leveraging multiple dispatch in Julia, we have
successfully applied this technique to DynamicPPL programs in our package
TPGExplorers.jl\footnote{\url{https://github.com/Julia-Tempering/TPGExplorers.jl}}.

>>>>

But this is where Pigeons can help: within a PT run, PG can be
used to explore each distribution in the annealing path. We expect PG to work 
more effectively on tempered 
distributions closer to the prior. Such samples can then be transported towards 
the posterior chain via the PT process.
In order to construct this sequence of distributions for an arbitrary program in
a Turing-complete PPL, it suffices to inject an inverse temperature parameter 
$\beta\in[0,1]$ in the call to compute the log density of every \texttt{observe} 
statement in the program. Leveraging multiple dispatch in Julia, we have
successfully applied this technique to DynamicPPL programs in our package
TPGExplorers.jl\footnote{\url{https://github.com/Julia-Tempering/TPGExplorers.jl}}.
